Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-06-13 manuscripts/TCS2023/tcs2023.tex
Topology
Finished revising

For example, let us consider the Boolean network shown in Example~\ref{example:BN}.
Figure~\ref{fig:stg} shows the dynamics of this model under the fully asynchronous update \change{scheme} (i.e., only one node is updated at each time step).
The model has all two trap spaces, \(m_1 = 11\) and \(m_2 = \star\star\).
Since \(m_1 < m_2\), \(m_1\) is the only minimal trap space of the Boolean network.

@@

\begin{figure}[!htb]
\centering
\begin{subfigure}[b]{0.3\textwidth}
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, every node/.style={scale=1.0}]
   \node[] (0) [] {00};
   \node[] (1) [above=of 0] {01};
   \node[] (2) [right=of 0] {10};
   \node[] (3) [above=of 2] {11};

@@

   \draw[->] (3) edge [loop right] (3);
\end{tikzpicture}
\caption{State transition graph, under the fully asynchronous update \change{scheme}.}%
\label{fig:stg}
\end{subfigure}\hfill%
\begin{subfigure}[b]{0.6\textwidth}
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, every node/.style={scale=1.0}]\footnotesize
  \node[circle,draw,label=left:$p_{x_1}$] (x1) {};
  \node[circle,draw,label=left:$\overline{p}_{x_1}$] (nx1) [below=of x1, yshift=-0.5cm] {};

@@

  \draw[->] (nx2) -- (t1x2);
  \draw[->] (t1x2) -- (x2);
  \draw[<->] (t1x2) -- (nx1);
\end{tikzpicture}
\caption{Petri net encoding of the model. Circles denote places, whereas rectangles denote transitions.}%
\label{fig:PN}
\end{subfigure}%
\caption{Dynamics and encoding of the Boolean network of Example~\ref{example:BN}.}%
\label{fig:stg_and_PN}
\end{figure}

>>>>

For example, let us consider the Boolean network shown in Example~\ref{example:BN}.
\change{Figure~\ref{fig:stg}} shows the dynamics of this model under the fully asynchronous update \change{scheme} (i.e., only one node is updated at each time step).
The model has all two trap spaces, \(m_1 = 11\) and \(m_2 = \star\star\).
Since \(m_1 < m_2\), \(m_1\) is the only minimal trap space of the Boolean network.

@@

\begin{figure}[!htb]
\centering
\begin{subfigure}[b]{0.25\textwidth}
  \centering
  \begin{tikzpicture}
    \node (1) {\(x_{1}\)};
    \node (2) [right=of 1] {\(x_{2}\)};

    \draw[->] (1) edge [bend left=45] (2);
    \draw[->] (2) edge [bend left=45] (1);
    \draw[->] (1) to [loop left] (1);
    \draw[->] (2) to [loop right] (2);
  \end{tikzpicture}
  \caption{\change{Influence graph of the model. Each arc is actually both positive and negative.}}
\end{subfigure}\hfill%
\begin{subfigure}[b]{0.25\textwidth}
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, every node/.style={scale=1.0}]
   \node[] (0) [] {00};
   \node[] (1) [above=of 0] {01};
   \node[] (2) [right=of 0] {10};
   \node[] (3) [above=of 2] {11};

@@

   \draw[->] (3) edge [loop right] (3);
\end{tikzpicture}
\caption{State transition graph, under the fully asynchronous update \change{scheme}.}%
\label{fig:stg}
\end{subfigure}\hfill%
\begin{subfigure}[b]{0.4\textwidth}
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, every node/.style={scale=1.0}]\footnotesize
  \node[circle,draw,label=left:$p_{x_1}$] (x1) {};
  \node[circle,draw,label=left:$\overline{p}_{x_1}$] (nx1) [below=of x1, yshift=-0.5cm] {};

@@

  \draw[->] (nx2) -- (t1x2);
  \draw[->] (t1x2) -- (x2);
  \draw[<->] (t1x2) -- (nx1);
\end{tikzpicture}
\caption{Petri net encoding of the model. Circles denote places, whereas rectangles denote transitions.}%
\label{fig:PN}
\end{subfigure}\hfill%
\caption{\change{Influence graph, dynamics, and Petri net encoding of the Boolean network of Example~\ref{example:BN}}.}%
\label{fig:stg_and_PN}
\end{figure}
